Fast solvers for partial differential equations \\ subject to inequalities

### 2023-11-04 talk-dms/references.tex
basic slides by copy of oxford talk ... much to do

\newcommand{\sdoi}[1]{\,{\tiny \href{https://doi.org/#1}{doi:#1}}}
\begin{itemize}
\item A.~Brandt \& C.~Cryer (1983). \emph{Multigrid algorithms for the solution of linear complementarity problems \dots}, SIAM J.~Sci.~Stat.~Comput.~4 (4), 655--684 \sdoi{10.1137/0904046}
%FTITLE Multigrid algorithms for the solution of linear complementarity problems arising from free boundary problems
\item P.~Brune, M.~Knepley, B.~Smith, \& X.~Tu (2015). \emph{Composing scalable nonlinear algebraic solvers}, SIAM Review~57 (4), 535--565 \sdoi{10.1137/130936725}
\item E.~Bueler (2021). \emph{Conservation laws for free-boundary fluid layers}, SIAM J.~Appl.~Math.~81 (5), 2007--2032 \sdoi{10.1137/20M135217X}
%\item E.~Bueler (2022). \emph{Performance analysis of high-resolution ice-sheet simulations}, J.~Glaciol., \sdoi{10.1017/jog.2022.113}
\item G.~Gonzalez de Diego, P.~Farrell, \& I.~Hewitt (2022). \emph{Numerical approximation of viscous contact problems applied to glacial sliding}, J.~Fluid Mech.~938 (A21). \sdoi{10.1017/jfm.2022.178}
\item P.~Farrell, M.~Croci, \& T.~Surowiec (2020). \emph{Deflation for semismooth equations}, Optimization Methods \& Software 35 (6), 1248--1271 \sdoi{10.1080/10556788.2019.1613655}
\item C.~Gr{\"a}ser \& R.~Kornhuber (2009). \emph{Multigrid methods for obstacle problems}, J.~Comput.~Math., 1--44
%\item T.~Isaac, G.~Stadler, \& O.~Ghattas (2015). \emph{Solution of nonlinear Stokes equations \dots ice sheet dynamics}, SIAM J.~Sci.~Comput., 37 (6), B804--B833 \sdoi{10.1137/140974407}
%FTITLE Solution of nonlinear Stokes equations discretized by high-order finite elements on nonconforming and anisotropic meshes, with application to ice sheet dynamics
\item G.~Jouvet \& E.~Bueler (2012). \emph{Steady, shallow ice sheets as obstacle problems \dots}, SIAM J.~Appl.~Math.~72 (4), 1292--1314 \sdoi{10.1137/110856654}
%FTITLE Steady, shallow ice sheets as obstacle problems: well-posedness and finite element approximation
%\item G.~Jouvet \& J.~Rappaz (2011). \emph{Analysis and finite element approximation of a nonlinear stationary {S}tokes problem \dots}, Adv.~Numer.~Analysis 2011 (164581) \sdoi{10.1155/2011/164581}
%FTITLE Analysis and finite element approximation of a nonlinear stationary {S}tokes problem arising in glaciology
\item R.~Kornhuber (1994). \emph{Monotone multigrid methods for elliptic variational inequalities I}, Numer.~Math.~69, 167--184 \sdoi{10.1007/BF03325426}
\item A.~Reusken (1987). \emph{Convergence of the multigrid full approximation scheme \dots}, Numer.~Math.~52, 251--277 \sdoi{10.1007/BF01398879}
%FTITLE Convergence of the multigrid full approximation scheme for a class of elliptic mildly nonlinear boundary value problems
%\item J.~Seguinot \& 5 others (2018).  \emph{Modelling last glacial cycle ice dynamics in the Alps}, The Cryosphere, 12 (10), 3265--3285 \sdoi{10.5194/tc-12-3265-2018}
%FAUTHORS Seguinot, J., Ivy-Ochs, S., Jouvet, G., Huss, M., Funk, M., & Preusser, F.
\item X.~Tai (2003). \emph{Rate of convergence for some constraint decomposition methods for nonlinear variational inequalities}, Numer.~Math.~93 (4), 755--786 \sdoi{10.1007/s002110200404}
\end{itemize}

>>>>

\newcommand{\sdoi}[1]{\,{\tiny \href{https://doi.org/#1}{doi:#1}}}
\begin{itemize}
\item A.~Brandt (1977). \emph{Multi-level adaptive solutions to boundary-value problems}, Mathematics of Computation 31 (138), 333--390
%\item A.~Brandt \& C.~Cryer (1983). \emph{Multigrid algorithms for the solution of linear complementarity problems \dots}, SIAM J.~Sci.~Stat.~Comput.~4 (4), 655--684 \sdoi{10.1137/0904046}
%%FTITLE Multigrid algorithms for the solution of linear complementarity problems arising from free boundary problems
%\item P.~Brune, M.~Knepley, B.~Smith, \& X.~Tu (2015). \emph{Composing scalable nonlinear algebraic solvers}, SIAM Review~57 (4), 535--565 \sdoi{10.1137/130936725}
\item E.~Bueler (2021). \emph{Conservation laws for free-boundary fluid layers}, SIAM J.~Appl.~Math.~81 (5), 2007--2032 \sdoi{10.1137/20M135217X}
%\item E.~Bueler (2022). \emph{Performance analysis of high-resolution ice-sheet simulations}, J.~Glaciol., \sdoi{10.1017/jog.2022.113}
\item E.~Bueler \& P.~Farrell (2023).  \emph{A full approximation storage multilevel method for nonlinear variational inequalities}, submitted \, {\tiny \href{https://arxiv.org/abs/2308.06888}{arxiv:2308.06888}}
%\item G.~Gonzalez de Diego, P.~Farrell, \& I.~Hewitt (2022). \emph{Numerical approximation of viscous contact problems applied to glacial sliding}, J.~Fluid Mech.~938 (A21). \sdoi{10.1017/jfm.2022.178}
%\item P.~Farrell, M.~Croci, \& T.~Surowiec (2020). \emph{Deflation for semismooth equations}, Optimization Methods \& Software 35 (6), 1248--1271 \sdoi{10.1080/10556788.2019.1613655}
\item C.~Gr{\"a}ser \& R.~Kornhuber (2009). \emph{Multigrid methods for obstacle problems}, J.~Comput.~Math., 1--44
%\item T.~Isaac, G.~Stadler, \& O.~Ghattas (2015). \emph{Solution of nonlinear Stokes equations \dots ice sheet dynamics}, SIAM J.~Sci.~Comput., 37 (6), B804--B833 \sdoi{10.1137/140974407}
%FTITLE Solution of nonlinear Stokes equations discretized by high-order finite elements on nonconforming and anisotropic meshes, with application to ice sheet dynamics
\item G.~Jouvet \& E.~Bueler (2012). \emph{Steady, shallow ice sheets as obstacle problems: well-posedness and finite element approximation}, SIAM J.~Appl.~Math.~72 (4), 1292--1314 \sdoi{10.1137/110856654}
%\item G.~Jouvet \& J.~Rappaz (2011). \emph{Analysis and finite element approximation of a nonlinear stationary {S}tokes problem \dots}, Adv.~Numer.~Analysis 2011 (164581) \sdoi{10.1155/2011/164581}
%FTITLE Analysis and finite element approximation of a nonlinear stationary {S}tokes problem arising in glaciology
%\item R.~Kornhuber (1994). \emph{Monotone multigrid methods for elliptic variational inequalities I}, Numer.~Math.~69, 167--184 \sdoi{10.1007/BF03325426}
\item A.~Reusken (1987). \emph{Convergence of the multigrid full approximation scheme for a class of elliptic mildly nonlinear boundary value problems}, Numer.~Math.~52, 251--277 \sdoi{10.1007/BF01398879}
%\item J.~Seguinot \& 5 others (2018).  \emph{Modelling last glacial cycle ice dynamics in the Alps}, The Cryosphere, 12 (10), 3265--3285 \sdoi{10.5194/tc-12-3265-2018}
%FAUTHORS Seguinot, J., Ivy-Ochs, S., Jouvet, G., Huss, M., Funk, M., & Preusser, F.
\item X.~Tai (2003). \emph{Rate of convergence for some constraint decomposition methods for nonlinear variational inequalities}, Numer.~Math.~93 (4), 755--786 \sdoi{10.1007/s002110200404}
\end{itemize}

### 2023-11-04 talk-dms/slides.tex
basic slides by copy of oxford talk ... much to do

\title[Multigrid for nonlinear and nonlocal VIs]{Toward nonlinear multigrid \\ for nonlinear and nonlocal variational inequalities}

@@

\date[]{February 2023}

@@

\titlegraphic{\hfill \includegraphics[width=0.15\textwidth]{images/uafbw.png} \quad \includegraphics[width=0.10\textwidth]{images/oxford.png}}

@@

{
  %\usebackgroundtemplate{\includegraphics[width=\paperwidth]{images/gray-british-clark2022.png}}
  \begin{frame}
    \titlepage
  \end{frame}
}

\begin{frame}{Outline}
  \tableofcontents[hideallsubsections]
\end{frame}

@@

\includegraphics[width=0.55\textwidth]{images/obstacle65.pdf} \qquad \includegraphics[width=0.35\textwidth]{images/obstacle-sets.png}

@@

\begin{center}
\includegraphics[width=0.9\textwidth]{images/calcone.png}
\end{center}
\end{frame}

@@

\section{full approximation scheme (FAS) multigrid for PDEs}

@@

\begin{center}
$\Omega^h$\, \includegraphics[height=0.16\textheight]{images/fine-grid.png} \hspace{25mm} \includegraphics[height=0.16\textheight]{images/coarse-grid.png} \,$\Omega^H$
\end{center}

@@

\includegraphics[height=0.15\textheight]{images/mg-grids.png}

@@

\only<1>{
\hfill \includegraphics[height=0.15\textheight]{images/mg-vcycle.png}
}
\only<2>{\hfill \includegraphics[height=0.15\textheight]{images/mg-fcycle.png} \quad \begin{tabular}{l} F-cycle = \\ nested iteration \end{tabular}
}

@@

\begin{frame}[fragile]
\frametitle{multigrid solver composition in PETSc}

\begin{itemize}
\item implemented here using an FD discretization and PETSc:\footnote{Portable Extensible Toolkit for Scientific computing \quad \href{https://petsc.org/release/}{\texttt{petsc.org}} \quad \includegraphics[height=3mm]{images/petsc.png}}
    \begin{itemize}
    \item[$\circ$] multigrid solvers in PETSc are \emph{composed} from smoothers on each level, and a coarse-level solver \dots here these are nonlinear GS
    \item[$\circ$] FAS multigrid is a nonlinear solver (SNES) type
    \item[$\circ$] PETSc $=$ C/Fortran/python
    \end{itemize}
\item FAS multigrid F-cycle:
\end{itemize}
\begin{Verbatim}[xleftmargin=15mm,fontsize=\scriptsize]
./bratu -da_grid_x 5 -da_grid_y 5 -da_refine J \
    -snes_rtol 1.0e-12 \
    -snes_type fas \
    -snes_fas_type full \
    -fas_levels_snes_type ngs \
    -fas_levels_snes_ngs_sweeps 2 \
    -fas_levels_snes_ngs_max_it 1 \
    -fas_levels_snes_norm_schedule none \
    -fas_coarse_snes_type ngs \
    -fas_coarse_snes_max_it 1 \
    -fas_coarse_snes_ngs_sweeps 4 \
    -fas_coarse_snes_ngs_max_it 1 
\end{Verbatim}

%NOT IN MY BOOK \hfill \includegraphics[width=8mm]{images/frontcover.jpg}
\end{frame}

@@

\begin{columns}
\begin{column}{0.45\textwidth}
\begin{itemize}
\item observed optimality:
\begin{align*}
\text{flops} &= O(N^1) \\
\text{exp evaluations} &= O(N^1) \\
\text{processor time} &= O(N^1)
\end{align*}
\item<1-> up to $N\approx 10^8$ dofs
    \begin{itemize}
    \item[$\circ$] $J=11$ refinements
    \item[$\circ$] laptop is memory-limited
    \end{itemize}
\item<2> compare $\approx 20\,\mu\,\text{s}/\text{N}$ for Poisson equation using Firedrake $P_1$ elements and geometric multigrid
\end{itemize}
\end{column}
\begin{column}{0.55\textwidth}
\includegraphics<1>[width=\textwidth]{images/bratu-exps.png}

\includegraphics<2>[width=\textwidth]{images/bratu-time.png}
\end{column}
\end{columns}
\end{frame}

@@

\section{the nonlinear and nonlocal VI for a fluid layer in a climate}

@@

\bigskip
\hfill \mbox{\includegraphics[height=0.25\textheight]{images/domain-data.png} \hspace{7mm} \includegraphics[height=0.25\textheight]{images/domain-velocity.png}}
\end{frame}

@@

\includegraphics[width=1.02\textwidth]{images/alps-seguinot2018.png}

@@

\bigskip
\hfill \mbox{\includegraphics[height=0.2\textheight]{images/domain-data.png} \hspace{7mm} \includegraphics[height=0.2\textheight]{images/domain-velocity.png}}
\end{frame}

@@

\begin{itemize}
\only<1>{
\item \alert{Stokes model}

solve the Stokes problem, then evaluate velocity at surface:
    $$\int_{\Lambda(s) = \{b < z <s\}} 2 \nu(D\bu) D\bu : D\bv - p \Div\bv - (\Div\bu) q - \rhoi \bg \cdot \bv = 0 \quad \forall \bv,q$$
    $$\Phi(s) = - \bu|_s \cdot \bn_s$$

    \begin{itemize}
    \item[$\circ$] assuming incompressibility and non-Newtonian viscosity: $\nu(D\bu) = \frac{1}{2} \Gamma |D\bu|^{\pp-2}$ with $\pp = \frac{4}{3}$
    \item[$\circ$] given $s$, this is a well-posed problem for velocity $\bu\in \mathbf{W}^{1,\pp}$ and pressure $p \in L^\qq$ on domain $\Lambda(s)$
    \item[$\circ$] near-optimal solvers available (Isaac et al 2015)
    \end{itemize}
}

\only<2>{
\item \alert{lubrication approximation}\footnote{also known as the \emph{shallow ice approximation}} \alert{model}

apply a nonlinear elliptic differential operator to $s$:
    $$\Phi(s) = - \frac{\gamma}{\qq} (s-b)^{\qq} |\grad s|^{\qq} - \grad \cdot\left(\frac{\gamma}{\qq+1} (s-b)^{\qq+1} |\grad s|^{\qq-2} \grad s\right)$$
    \begin{itemize}
    \item $\qq = 4$
    \item $\grad$ is in $x,y$ only
    \item $\Phi(s)$ is a nonlinear \alert{differential operator} in this model because membrane stresses are \emph{not} balanced
    \item $\Phi(s)$ is doubly-degenerate
    \end{itemize}
}
\end{itemize}
\end{frame}

@@

\begin{frame}{CP form of viscous fluid layer in a climate}

\begin{itemize}
\item VI form on previous slide is too abstracted for clarity
\item the strong form of the same problem is a \alert{complementarity problem (CP) coupled to a Stokes problem}:
\begin{align*}
s - b &\ge 0 && \text{ in $\Omega \subset \RR^2$} \\
- \bu|_s \cdot \bn_s - a &\ge 0 && \text{''} \\
(s-b)(- \bu|_s \cdot \bn_s - a) &= 0 && \text{''} \\
- \nabla \cdot \left(2 \nu(D\bu)\, D\bu\right) + \nabla p - \rhoi \mathbf{g} &= \bzero && \text{in $\Lambda(s) \subset \RR^3$} \\
\nabla \cdot \bu &= 0 && \text{''} \\
\left(2 \nu(D\bu) D\bu - pI\right) \bn &= \bzero && \{z=s\} \subset \partial \Lambda(s) \\
\bu &= \bzero && \{z=b\} \subset \partial \Lambda(s)
\end{align*}
\item solve this for $s$ on $\Omega$, and simultaneously for $\bu,p$ on $\Lambda(s) = \{b < z < s\}$
\end{itemize}
\end{frame}

\begin{frame}{a non-local VI problem}

\begin{itemize}
\item in the Stokes case, the residual $r(s) = a - \Phi(s)$ $= a + \bu|_s \cdot \bn_s$ \alert{depends non-locally on $s$}
\item for example, consider $\bu_{(s+\psi)} - \bu_{(s)}$ from surface perturbation

(hat function) $\psi$
\end{itemize}

\medskip
\begin{center}
\includegraphics[width=0.85\textwidth]{images/stokes-greens-arndt.png}
\end{center}

\vspace{-5mm}
\hfill {\tiny P.~Arndt figure}
\end{frame}

\begin{frame}{what's needed for multigrid to work here?}

\begin{block}{viscous fluid layer geometry problem}
	$$\ip{\Phi(s)}{r-s} \ge \ip{a}{r-s} \quad \text{ for all } r \in \mathcal{K}$$
where
\begin{itemize}
\item $\mathcal{K} = \left\{r \in \mathcal{V} \,:\, r \ge b\right\}$
\item $\Phi(s)=- \bu|_s \cdot \bn_s$
\item $s$ is solution surface elevation
\item $\bu$ is Stokes solution on $\Lambda(s) = \{b < z < s\}$
\item $a$ (climate) and $b$ (bed elevation) are the input data
\end{itemize} 
\end{block}

\begin{itemize}
\item[]
    \begin{itemize}
    \item[$\circ$] for more on this problem class see (Bueler, 2021)
    \end{itemize}
\end{itemize}

\begin{itemize}
\item {\color{FireBrick} what is needed for scalable multilevel solutions?}
    \begin{enumerate}
    \item[1.] iterates must be admissible
    \item[2.] global linearization of $\Phi(s)$ must be avoided
    \item[3.] smoother cost must be comparable to one residual    
    \end{enumerate}
\end{itemize}
\end{frame}

\section{multigrid approaches for VIs}

@@

\medskip
\hspace{10mm} \includegraphics[height=0.2\textheight]{images/obstacle65.pdf}

\vspace{-20mm}
\hfill \includegraphics[height=0.25\textheight]{images/vi-newton-gmg-bad.png}
\end{frame}

@@

\vspace{-12mm}
\hfill \includegraphics[width=0.25\textwidth]{images/mg-fcycle.png}
\end{itemize}

\bigskip
\includegraphics[height=0.25\textheight]{images/vi-newton-gmg-good.png}

\vspace{-22mm}
\hspace{40mm} \includegraphics[height=0.45\textheight]{images/obstacle-flops-per-n.png} \qquad \includegraphics<2>[width=20mm]{images/frontcover.jpg}
\end{frame}

\begin{frame}{multigrid strategies for VIs}

\begin{itemize}
\item semi-smooth Newton also yields mesh-independent iterations
    \begin{itemize}
    \item[$\circ$] penalty scaling argument (Farrell et al.~2020)
    \end{itemize}
\item other VI multilevel strategies:
    \begin{itemize}
    \item[$\circ$] projected FAS multigrid for linear CPs (Brandt \& Cryer, 1983)
    \item[$\circ$] monotone multigrid (Kornhuber, 1994)
    \item[$\circ$] multilevel constraint decomposition (Tai, 2003)  \hfill $\gets$ \emph{more below}
    \end{itemize}
\end{itemize}
\end{frame}

@@

\section{FAS multigrid for VIs?}

@@

\vspace{-25mm}
\hfill \includegraphics[width=0.4\textwidth]{images/fascd-vcycle.png}
\end{frame}

\begin{frame}{as decomposition of the fluid layer}

\begin{itemize}
\item again this is too abstract
\item what does it look like for the fluid layer?
    \begin{itemize}
    \item[$\circ$] coarse grids have \emph{admissible} pieces of the fine-grid iterate
    \end{itemize}
\end{itemize}

\bigskip
\begin{center}
\includegraphics[width=\textwidth]{images/icedecomp.png}
\end{center}
\end{frame}

@@

@@

\medskip
\begin{center}
\includegraphics[width=0.8\textwidth]{images/fascd-firedrake-dome.png}
\end{center}
\end{frame}

\begin{frame}{evidence of mesh independence}

\begin{itemize}
\item same lubrication approximation, but in 1D
\item FASCD V-cycles with NGS and NJacobi smoothers
\item up-smoothing preferred: V(0,2) beats V(1,1)
\item evidence of mesh independence of factors $\|r^{(k+1)}\| / \|r^{(k)}\|$
\end{itemize}

\begin{center}
\includegraphics[width=0.5\textwidth]{images/sia-asymprates.pdf}
\end{center}
\end{frame}

@@

\begin{itemize}
\item the \alert{variational inequality (VI)} problem class is good to know
\item likewise \alert{full approximation storage (FAS) multigrid}
    \begin{itemize}
    \item[$\circ$] need for better support and documentation in PETSc/Firedrake
    \end{itemize}
\item multigrid treatment of nonlinear and \alert{nonlocal VIs}?
    \begin{itemize}
    \item[$\circ$] smoothers not obvious in nonlocal cases
    \item[$\circ$] seeking practical evidence of mesh-independent convergence
    \end{itemize}
\item glacier evolution, as fluid-layer-in-climate problems, \alert{needs attention} from applied mathematicians and numerical analysts
    \begin{itemize}
    \item[$\circ$] VI form not widely recognized
    \item[$\circ$] current state of the art $=$ explicit time stepping of surface
        \begin{itemize}
        \item[$\vartriangleright$] slow for science, intrinsically \emph{not} scalable
        \end{itemize}
    \item[$\circ$] to do: \alert{steady-state and implicit step VI problems}
    \item[$\circ$] more on this view in my Math.~Geosci.~seminar tomorrow 2pm L5
    \end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{additional background references}

>>>>

\title[Fast solvers for PDEs subject to inequalities]{Fast solvers for partial differential equations \\ subject to inequalities}

@@

\date[]{November 2023}

@@

\titlegraphic{\vspace{-8mm} \includegraphics[width=0.25\textwidth]{../talk-oxford/images/uafbw.png} \hfill \begin{minipage}{0.16\textwidth}
\includegraphics[width=\textwidth]{../talk-oxford/images/oxford.png}

\vspace{18mm}
\end{minipage} \vspace{-10mm}}

@@

{
  %\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../talk-oxford/images/gray-british-clark2022.png}}
  \begin{frame}
    \titlepage
  \end{frame}
}

\begin{frame}{Outline}
  %\tableofcontents[hideallsubsections]
  \tableofcontents
\end{frame}

@@

\includegraphics[width=0.55\textwidth]{../talk-oxford/images/obstacle65.pdf} \qquad \includegraphics[width=0.35\textwidth]{../talk-oxford/images/obstacle-sets.png}

@@

\begin{center}
\includegraphics[width=0.9\textwidth]{../talk-oxford/images/calcone.png}
\end{center}
\end{frame}

@@

\section{multigrid for PDEs}

\subsection{nonlinear multigrid = full approximation scheme (FAS)}

@@

\begin{center}
$\Omega^h$\, \includegraphics[height=0.16\textheight]{../talk-oxford/images/fine-grid.png} \hspace{25mm} \includegraphics[height=0.16\textheight]{../talk-oxford/images/coarse-grid.png} \,$\Omega^H$
\end{center}

@@

\includegraphics[height=0.15\textheight]{../talk-oxford/images/mg-grids.png}

@@

\only<1>{
\hfill \includegraphics[height=0.15\textheight]{../talk-oxford/images/mg-vcycle.png}
}
\only<2>{\hfill \includegraphics[height=0.15\textheight]{../talk-oxford/images/mg-fcycle.png} \quad \begin{tabular}{l} F-cycle = \\ nested iteration \end{tabular}
}

@@

@@

\begin{columns}
\begin{column}{0.45\textwidth}
\begin{itemize}
\item observed optimality:
\begin{align*}
\text{flops} &= O(N^1) \\
\text{exp evaluations} &= O(N^1) \\
\text{processor time} &= O(N^1)
\end{align*}
\item<1-> up to $N\approx 10^8$ dofs
    \begin{itemize}
    \item[$\circ$] $J=11$ refinements
    \item[$\circ$] laptop is memory-limited
    \end{itemize}
\item<2> compare $\approx 20\,\mu\,\text{s}/\text{N}$ for Poisson equation using Firedrake $P_1$ elements and geometric multigrid
\end{itemize}
\end{column}
\begin{column}{0.55\textwidth}
\includegraphics<1>[width=\textwidth]{../talk-oxford/images/bratu-exps.png}

\includegraphics<2>[width=\textwidth]{../talk-oxford/images/bratu-time.png}
\end{column}
\end{columns}
\end{frame}

@@

@@

\bigskip
\hfill \mbox{\includegraphics[height=0.25\textheight]{../talk-oxford/images/domain-data.png} \hspace{7mm} \includegraphics[height=0.25\textheight]{../talk-oxford/images/domain-velocity.png}}
\end{frame}

@@

\includegraphics[width=1.02\textwidth]{../talk-oxford/images/alps-seguinot2018.png}

@@

\bigskip
\hfill \mbox{\includegraphics[height=0.2\textheight]{../talk-oxford/images/domain-data.png} \hspace{7mm} \includegraphics[height=0.2\textheight]{../talk-oxford/images/domain-velocity.png}}
\end{frame}

@@

\begin{itemize}
\item \alert{lubrication approximation}\footnote{also known as the \emph{shallow ice approximation}} \alert{model}

apply a nonlinear elliptic differential operator to $s$:
    $$\Phi(s) = - \frac{\gamma}{\qq} (s-b)^{\qq} |\grad s|^{\qq} - \grad \cdot\left(\frac{\gamma}{\qq+1} (s-b)^{\qq+1} |\grad s|^{\qq-2} \grad s\right)$$
    \begin{itemize}
    \item $\qq = 4$
    \item $\grad$ is in $x,y$ only
    \item $\Phi(s)$ is a nonlinear \alert{differential operator} in this model because membrane stresses are \emph{not} balanced
    \item $\Phi(s)$ is doubly-degenerate
    \end{itemize}
\end{itemize}
\end{frame}

@@

\section{multigrid for VIs}

\subsection{earlier approaches}

@@

\medskip
\hspace{10mm} \includegraphics[height=0.2\textheight]{../talk-oxford/images/obstacle65.pdf}

\vspace{-20mm}
\hfill \includegraphics[height=0.25\textheight]{../talk-oxford/images/vi-newton-gmg-bad.png}
\end{frame}

@@

\vspace{-12mm}
\hfill \includegraphics[width=0.25\textwidth]{../talk-oxford/images/mg-fcycle.png}
\end{itemize}

\bigskip
\includegraphics[height=0.25\textheight]{../talk-oxford/images/vi-newton-gmg-good.png}

\vspace{-22mm}
\hspace{40mm} \includegraphics[height=0.45\textheight]{../talk-oxford/images/obstacle-flops-per-n.png} \qquad \includegraphics<2>[width=20mm]{../talk-oxford/images/frontcover.jpg}
\end{frame}

@@

\subsection{full approximation scheme constraint decomposition (FASCD)}

@@

\vspace{-25mm}
\hfill \includegraphics[width=0.4\textwidth]{../talk-oxford/images/fascd-vcycle.png}
\end{frame}

@@

\section{results}

\subsection{classical obstacle problem}

\subsection{advection-diffusion of a concentration}

\subsection{glacier surface elevations}

@@

\medskip
\begin{center}
\includegraphics[width=0.8\textwidth]{../talk-oxford/images/fascd-firedrake-dome.png}
\end{center}
\end{frame}

\begin{frame}{mesh independence}

\begin{itemize}
\item FIXME
\end{itemize}
\end{frame}

@@

\begin{itemize}
\item FIXME
\end{itemize}
\end{frame}

@@

\begin{frame}{background references}
